\def\newblock{\hskip .11em plus.33em minus.07em}


\usepackage[english]{babel}
\usepackage[space]{grffile}
\usepackage{thmtools}
\usepackage{thm-restate}
\usepackage[export]{adjustbox}
\usepackage{
    algorithm,
    algorithmic,
    bibentry,
    bm,
    bookmark,
    booktabs,
    cancel,
    float,
    import,
    mathtools,
    natbib,
    pdflscape,
    subcaption,
    tikz,
    tikzscale,
    times
}
\usepackage[includefoot, bottom=0.5in]{geometry}
\usetikzlibrary{bayesnet}

\addto\extrasenglish{%
  \renewcommand{\chapterautorefname}{Chapter}%
} 

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{property}[theorem]{Property}

\newcommand{\algorithmautorefname}{Algorithm}

\import{notation/}{init.tex}

\newcommand{\ibhcack}{
\autoref{chap:ibhc}, in full, is a reprint of material
as it appears in ``Interactive Bayesian Hierarchical Clustering''. 
S. Vikram and S. Dasgupta.
In International Conference on Machine Learning 2016.
The dissertation author was the primary investigator.
}


\newcommand{\nvmpack}{
\autoref{chap:nvmp}, in full, contains
material that is currently being prepared for
submission for publication of the material.
S. Vikram.
The dissertation author is the primary investigator.
}

\newcommand{\loracsack}{
\autoref{chap:loracs}, in full, is a reprint of the
as it appears in
``The LORACs Prior for VAEs: Letting the Trees Speak for the Data''. 
S.Vikram, M. Hoffman, and M. Johnson. 
In International Conference on Artificial Intelligence and Statistics 2019.
The dissertation was the primary investigator.
}

\newcommand{\solarack}{
\autoref{chap:solar}, in full, is a reprint of material
as it appears in ``SOLAR: Deep Structured Representations for Model-Based Reinforcement Learning''.
M. Zhang*, S. Vikram*, L. Smith, P. Abbeel, M. Johnson, and S. Levine.
In International Conference on Machine Learning 2019.
The dissertation author was one of two primary investigators.
}
